Data Preparation, Integration and Cleaning

### 2018-05-08 scripts/3_data_prep.Rmd
Update to mapping.

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=TRUE)
```

@@

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)
  library(dplyr)
  library(multidplyr)
  library(lubridate)
  library(tidyverse)
  library(sf)

@@

  # Remove missing data
  ltr_tdf <- ltr_tdf %>% dplyr::filter(!is.na(baths))
  str_tdf <- str_tdf %>% dplyr::filter(!is.na(baths))

@@

   ltbath <- ggplot(ltr_tdf, aes(x=baths)) + 
     geom_bar(fill=ltr_col, color=ltr_col) +
     facet_wrap(~type) +
     scale_x_continuous(labels=1:8, breaks=1:8)+
     xlab('\nBathrooms\n') +
     ylab('') +
     ggtitle('Bathrooms in Long Term Rentals') +
     theme(plot.title = element_text(hjust = 0.5))

@@

  stbath <- ggplot(str_tdf, aes(x=baths)) +
    geom_bar(fill=str_col, color=str_col) +
    facet_wrap(~type, scales='free_y') +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') +
    ggtitle('Bathrooms in Short Term ltrals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr_tdf <- ltr_tdf %>%
    dplyr::rename(bathrooms = baths) %>%
    dplyr::filter(bathrooms < 4 & bathrooms > 0)

@@

# ```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
#  # Convert shapefile to ggplot-able object
#   # Fix lat/long
#   # Limit to extent of data
#   sub.table <- table(ltr_df$suburb)
#   sub.table <- sub.table[sub.table != 0]
#   # Clip to only those with a ltral observation
#   study.suburbs <- suburbs.shp[suburbs.shp@data$name_2006 %in% names(sub.table),]
#   # Convert to an outer bound with holes
#   ss.bound <- gUnaryUnion(study.suburbs)
#   # Remove holes from the shapefile
#   ssb <- slot(ss.bound, "polygons") 
#   holes <- lapply(ssb, function(x) sapply(slot(x, "Polygons"), 
#                                           slot, "hole"))
#   res <- lapply(1:length(ssb), function(i) slot(ssb[[i]], "Polygons")[!holes[[i]]]) 
#   IDs <- row.names(ss.bound) 
#   ssb.fill <- SpatialPolygons(lapply(1:length(res), function(i) 
#    Polygons(res[[i]], ID=IDs[i])), proj4string=CRS(proj4string(ss.bound))) 
#   # Identify which suburbs all in area covered by outer bound
#   ss.in <- gIntersects(suburbs.shp, ssb.fill, byid=T)
#   study.suburbs <- suburbs.shp[which(ss.in), ]
#   # Convert into an outer boundary with no holes
#   ss.bound.out <- gUnaryUnion(study.suburbs)
#   ssb.out <- slot(ss.bound.out, "polygons") 
#   holes <- lapply(ssb.out, function(x) sapply(slot(x, "Polygons"), 
#                                           slot, "hole"))
#   res.out <- lapply(1:length(ssb.out), 
#                     function(i) slot(ssb.out[[i]], "Polygons")[!holes[[i]]]) 
#   IDs <- row.names(ss.bound.out) 
#   ssb.fill.out <- SpatialPolygons(lapply(1:length(res.out), 
#                                          function(i) Polygons(res.out[[i]], 
#                                                               ID=IDs[i])),
#                                               proj4string=CRS(proj4string(ss.bound))) 
#   # Convert into a ggplot-able format
#   subs <- fortify(study.suburbs, region='name_2006')
#   # Add suburb category
#   subs$des <- suburbs.shp@data$suburbdesi[
#     match(subs$id, suburbs.shp@data$name_2006)]
# ```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
#  ## Build the map object
#   # Set colors
#   g_cols <- c('grey10', 'grey40', 'grey70')
#   loc.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
#     scale_fill_manual(values=g_cols, labels=c('Inner      ',
#                                               'Middle      ',
#                                               'Outer')) +
#     geom_path(data=subs[subs$des=='Outer', ], 
#               aes(x=long, y=lat, group=group), col='white', size=.1,
#               linetype=1) +
#     geom_path(data=subs[subs$des=='Middle', ], 
#               aes(x=long, y=lat, group=group), col='grey70', size=.1,
#               linetype=1) +
#     geom_path(data=subs[subs$des=='Inner', ], 
#               aes(x=long, y=lat, group=group), col='grey40', size=.1,
#               linetype=1) +
#     #ggtitle("Melbourne Suburb Classifications")+
# ```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=6}
#   png(file=paste0(fig.path, 'locationmap.png'), width = 480, height = 390, 
#     loc.map
#   loc.map
#   save(loc.map, file=paste0(fig.path, 'suburbMap.RData'))
# It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.  While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.  Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:
# 1. Rural (Outer suburbs, not Beach)
# 2. Suburban (Middle suburbs, not Beach)
# 3. City (Inner Suburbs, not Beach, not Core)
# 4. City-Core (Select inner suburbs with tourist activities and near CBD)
# 5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)
# We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.  This process is repeated for both the short and long term data.  We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on. Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs). 
# We select the 18 suburbs below to represent the 'core' of the city.  The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.  All are well serviced by public transportation and possess abundant amenties for tourists. 
# ```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
#  core.suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
#                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
#                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
#                    'St Kilda West', 'West Melbourne', 'Windsor')
# We then apply a 500 meter buffer to the beach along Port Phillip Bay. 
# ```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
#  # Determine centroid of study area
#   latMid <- median(str_df$latitude)
#   longMid <- median(str_df$longitude)
#  # Calculate Degress to Meters conversion 
#   m.lat = 111132.954 - 559.822 * cos(2 * latMid) + 1.175 * cos(4 * latMid)
#   m.long = 111132.954 * cos (latMid)
#   m.conv <- mean(m.lat, m.long)
#  # Create the beach buffer  
#   beach.buffer <- gBuffer(beach.shp, byid=FALSE, width=500/m.conv)
# Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.  
# ```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
#   # Convert to point shapefile
#   str.prop.shp <- SpatialPointsDataFrame(cbind(str_df$longitude,
#                                                str_df$latitude),
#                                          str_df,
#                                          proj4string=CRS("+init=epsg:4283")) 
#   # Add suburb name 
#   spJoin <- over(str.prop.shp, suburbs.shp)
#   str_df$suburb <- as.character(spJoin$name_2006)
#   str_df$suburb[is.na(str_df$suburb)] <- 'missing'
#   # Add suburb designation
#   str_df$sub.class <- as.character(spJoin$suburbdesi)
#   str_df$sub.class[is.na(str_df$sub.class)] <- 'missing'
#   # Add SA1 designation
#   spJoin <- over(str.prop.shp, sa1s.shp)
#   str_df$sa1 <- spJoin$sa1_main11
#   ## Add Beach Designation
#   spJoin <- over(str.prop.shp, beach.buffer)
#   str_df$beach <- ifelse(is.na(spJoin), 0 ,1)
#   # Remove those missing a suburb classification (out of area)
#   str_df <- str_df[str_df$sub.class != 'missing', ]
#   str_df <- str_df[str_df$sa1 != 'missing', ]
# ```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
#  ## Add the submarket designations
#   # Add individual classes
#   str_df$geo.mrkt <- 'rural'
#   str_df$geo.mrkt[str_df$sub.class == 'Middle'] <- 'suburban'
#   str_df$geo.mrkt[str_df$sub.class == 'Inner'] <- 'city'
#   str_df$geo.mrkt[str_df$suburb %in% core.suburbs] <- 'city-core'
#   str_df$geo.mrkt[str_df$beach == 1] <- 'beach'
#   # Order the factors properly
#   str_df$geo.mrkt <- factor(str_df$geo.mrkt, 
#                               levels=c('city-core', 'city', 'suburban', 
#                                         'rural', 'beach'))
# Before we do the same for the long term data, we must remedy the fact that about 5% of the long term rental observations have missing latitude and longitude values.  Half of these do, however, have a lat/long value for the centroid of the street that the property faces.  To retain as many observations as possible in these intial steps for those properties that lack a specific lat/long value we apply the street centroid value.  For those without either (3% of the total) we remove them from the dataset at this point. 
# ```{r fix_ltt_geo, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
#  # Label those missing lat/long  
#   miss.LL <- which(is.na(ltr_df$latitude))  
#  # Create a field to indicate the approximate matches  
#   ltr_df$miss.LL <- 0
#   ltr_df$miss.LL[miss.LL] <- 1
#  # Apply approximate match    
#   ltr_df$latitude[miss.LL] <- ltr_df$street.latitude[miss.LL]
#   ltr_df$longitude[miss.LL] <- ltr_df$street.longitude[miss.LL]
#  # Remove those still missing latitude data   
#   ltr_df <- ltr_df[!is.na(ltr_df$latitude), ]
# Having fixed the missing lat/long issue, we then assign the suburb, SA1, city-core and beach designations to observations in the long term rental dataset.  
# ```{r add_lt_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
#   # Long term data  
#   # Convert to point shapefile
#   ltr.prop.shp <- SpatialPointsDataFrame(cbind(ltr_df$longitude,
#                                                ltr_df$latitude),
#                                          ltr_df,
#                                          proj4string=CRS("+init=epsg:4283")) 
#   # Add suburb name 
#   spJoin <- over(ltr.prop.shp, suburbs.shp)
#   ltr_df$suburb <- as.character(spJoin$name_2006)
#   ltr_df$suburb[is.na(ltr_df$suburb)] <- 'missing'
#   # Add suburb designation
#   ltr_df$sub.class <- as.character(spJoin$suburbdesi)
#   ltr_df$sub.class[is.na(ltr_df$sub.class)] <- 'missing'
#   # Add SA1 designation
#   spJoin <- over(ltr.prop.shp, sa1s.shp)
#   ltr_df$sa1 <- spJoin$sa1_main11
#   ## Add Beach Designation
#   spJoin <- over(ltr.prop.shp, beach.buffer)
#   ltr_df$beach <- ifelse(is.na(spJoin), 0 ,1)
#   # Remove those missing a suburb classification (out of area)
#   ltr_df <- ltr_df[ltr_df$sub.class != 'missing', ]
#   ltr_df <- ltr_df[ltr_df$sa1 != 'missing', ]
# ```{r convert_lt_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
#  ## Add the submarket designations
#   # Add individual classes
#   ltr_df$geo.mrkt <- 'rural'
#   ltr_df$geo.mrkt[ltr_df$sub.class == 'Middle'] <- 'suburban'
#   ltr_df$geo.mrkt[ltr_df$sub.class == 'Inner'] <- 'city'
#   ltr_df$geo.mrkt[ltr_df$suburb %in% core.suburbs] <- 'city-core'
#   ltr_df$geo.mrkt[ltr_df$beach == 1] <- 'beach'
#   # Order the factors properly
#   ltr_df$geo.mrkt <- factor(ltr_df$geo.mrkt, 
#                               levels=c('city-core', 'city', 'suburban', 
#                                         'rural', 'beach'))
#   countCleaning('location')
# The location of the short and long term rentals, colored by submarket, are shown below
# ```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

>>>>

```{r setup, include=FALSE}
#knitr::opts_chunk$set(eval=TRUE)
```

@@

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  # library(Hmisc)
  library(multidplyr)
  library(lubridate)
  library(tidyverse)
  library(sf)

  options(stringsAsFactors=FALSE)

@@

  # Remove missing data
  ltr_tdf <- ltr_tdf %>%
    dplyr::rename(bathrooms = baths) %>%
    dplyr::filter(!is.na(bathrooms))
  str_tdf <- str_tdf %>% dplyr::filter(!is.na(bathrooms))

@@

   ltbath <- ggplot(ltr_tdf, aes(x=bathrooms)) + 
     geom_bar(fill=ltr_col, color=ltr_col) +
     facet_wrap(~type) +
     scale_x_continuous(labels=1:8, breaks=1:8)+
     xlab('\nBathrooms\n') +
     ylab('') +
     ggtitle('Bathrooms in Long Term Rentals') +
     theme(plot.title = element_text(hjust = 0.5))

@@

  stbath <- ggplot(str_tdf, aes(x=bathrooms)) +
    geom_bar(fill=str_col, color=str_col) +
    facet_wrap(~type, scales='free_y') +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') +
    ggtitle('Bathrooms in Short Term ltrals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr_tdf <- ltr_tdf %>%
    dplyr::filter(bathrooms < 4 & bathrooms > 0)

@@

```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Convert shapefile to ggplot-able object

   # Limit to extent of data
   ltr_subs <- ltr_tdf %>%
    dplyr::select(suburb) %>%
    group_by(suburb) %>%
    summarize(count=n())

   # Clip to only those with a ltral observation
   studysubs_sf <- sub_sf %>%
     filter(NAME_2006 %in% ltr_subs$suburb)

   # Convert to an outer bound with holes
   ss_bound <- st_union(studysubs_sf)

   # ss.bound <- gUnaryUnion(study.suburbs)
   # 
   # # Remove holes from the shapefile
   # ssb <- slot(ss.bound, "polygons") 
   # holes <- lapply(ssb, function(x) sapply(slot(x, "Polygons"), 
   #                                         slot, "hole"))
   # res <- lapply(1:length(ssb), function(i) slot(ssb[[i]], "Polygons")[!holes[[i]]]) 
   # IDs <- row.names(ss.bound) 
   # ssb.fill <- SpatialPolygons(lapply(1:length(res), function(i) 
   #  Polygons(res[[i]], ID=IDs[i])), proj4string=CRS(proj4string(ss.bound))) 
   # 
   # # Identify which suburbs all in area covered by outer bound
   # ss.in <- gIntersects(suburbs.shp, ssb.fill, byid=T)
   # study.suburbs <- suburbs.shp[which(ss.in), ]
   # 
   # # Convert into an outer boundary with no holes
   # ss.bound.out <- gUnaryUnion(study.suburbs)
   # ssb.out <- slot(ss.bound.out, "polygons") 
   # holes <- lapply(ssb.out, function(x) sapply(slot(x, "Polygons"), 
   #                                         slot, "hole"))
   # res.out <- lapply(1:length(ssb.out), 
   #                   function(i) slot(ssb.out[[i]], "Polygons")[!holes[[i]]]) 
   # IDs <- row.names(ss.bound.out) 
   # ssb.fill.out <- SpatialPolygons(lapply(1:length(res.out), 
   #                                        function(i) Polygons(res.out[[i]], 
   #                                                             ID=IDs[i])),
   #                                             proj4string=CRS(proj4string(ss.bound))) 
   # 
   # # Convert into a ggplot-able format
   # subs <- fortify(study.suburbs, region='name_2006')
   # 
   # # Add suburb category
   # subs$des <- suburbs.shp@data$suburbdesi[
   #   match(subs$id, suburbs.shp@data$name_2006)]

```{r mappoints2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

 ## Build the map object

#    # Set colors
#    g_cols <- c('grey10', 'grey40', 'grey70')
#  
#    # Make map
#    ggplot(studysubs_sf) %>%
#      geom_sf(aes(group=group, fill=suburbDesi))
# 
#    loc_map <- ggplot() +
#      geom_polygon(data=studysubs_sf, 
#                   aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
# #     scale_fill_manual(values=g_cols, labels=c('Inner      ',
#                                               'Middle      ',
#                                               'Outer')) +
#     geom_path(data=subs[subs$des=='Outer', ], 
#               aes(x=long, y=lat, group=group), col='white', size=.1,
#               linetype=1) +
#   
#     geom_path(data=subs[subs$des=='Middle', ], 
#               aes(x=long, y=lat, group=group), col='grey70', size=.1,
#               linetype=1) +
#     
#     geom_path(data=subs[subs$des=='Inner', ], 
#               aes(x=long, y=lat, group=group), col='grey40', size=.1,
#               linetype=1) +
#     
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     #ggtitle("Melbourne Suburb Classifications")+
#     theme(plot.title = element_text(hjust = 0.5))
# 
# ```
# 
# ```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=6}
#   png(file=paste0(fig.path, 'locationmap.png'), width = 480, height = 390, 
#       bg='transparent')
#   
#     loc.map
#     
#   dev.off()
#   
#   loc.map
#   
#   save(loc.map, file=paste0(fig.path, 'suburbMap.RData'))
# 
#     
```
# 
It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.  While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.  Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:

1. Rural (Outer suburbs, not Beach)
2. Suburban (Middle suburbs, not Beach)
3. City (Inner Suburbs, not Beach, not Core)
4. City-Core (Select inner suburbs with tourist activities and near CBD)
5. Beach (Properties within 500m of Port Phillip Bay east of Yarra River)

We assign these designations by: 1) Adding suburb designations to the properties; 2) Assigning submarkets 1-4 based on suburb location; and 3) Indicating proximity to beach and labeling as 'Beach' submarket.  This process is repeated for both the short and long term data.  We also add the Statistical Area 1 code for each property for use in additional spatial modeling later on. Finally, we also remove any observations that fall outside of outer suburbs (the extent of the suburbs).

We select the 18 suburbs below to represent the 'core' of the city.  The majority of tourist destinations and major events such as the Australian Open and the Grand Prix are located in these suburbs.  All are well serviced by public transportation and possess abundant amenties for tourists.

```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  core_suburbs <- c('Albert Park', 'Carlton', 'Collingwood', 'Cremorne', 'Docklands',
                    'East Melbourne', 'Fitzroy', 'Melbourne', 'Port Melbourne', 'Prahran',
                    'Richmond', 'South Melbourne', 'South Yarra', 'Southbank', 'St Kilda',
                    'St Kilda West', 'West Melbourne', 'Windsor')

We then apply a 500 meter buffer to the beach along Port Phillip Bay.

```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Determine centroid of study area

   lat_mid <- median(str_tdf$latitude)
   long_mid <- median(str_tdf$longitude)

 # Calculate Degress to Meters conversion

   m_lat = 111132.954 - 559.822 * cos(2 * lat_mid) + 1.175 * cos(4 * lat_mid)
   m_long = 111132.954 * cos (lat_mid)
   m_conv <- mean(c(m_lat, m_long))

  # Create the beach buffer

  beach_buffer <- st_buffer(beach_sf, dist =(500 / m_conv))

Next we assign the suburb, SA1, city-core and beach designations to observations in the Airbnb dataset.

```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Short term data

 # Convert to point shapefile
   str_tdf <- st_as_sf(str_tdf,
                       coords = c('longitude', 'latitude'),
                       crs = 4283)

   ltr_tdf <- st_as_sf(ltr_tdf %>% dplyr::filter(!is.na(latitude)),
                       coords = c('longitude', 'latitude'),
                       crs = 4283)

    str_tdf <- st_join(str_tdf, 
                       sub_sf %>% 
                        dplyr::select(suburb = NAME_2006,
                                      sub_des = suburbDesi,
                                      geometry)) %>%
    dplyr::filter(!is.na(sub_des))

    ltr_tdf <- st_join(ltr_tdf %>%
                         dplyr::select(-suburb), 
                       sub_sf %>% 
                        dplyr::select(suburb = NAME_2006,
                                      sub_des = suburbDesi,
                                      geometry)) %>%
    dplyr::filter(!is.na(sub_des))

    sub_str <- str_tdf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n())

    sub_ltr <- ltr_tdf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n())

    sub_all <- sub_ltr %>%
      dplyr::inner_join(sub_str, by='suburb')

    str_tdf <- str_tdf %>%
      dplyr::filter(suburb %in% sub_all$suburb)

    ltr_tdf <- ltr_tdf %>%
      dplyr::filter(suburb %in% sub_all$suburb)

    str_tdf <- st_join(str_tdf, 
                       sa1_sf %>%
                         dplyr::select(sa1=SA1_MAIN11,
                                       geometry)) %>%
    dplyr::filter(!is.na(sa1))

        ltr_tdf <- st_join(ltr_tdf, 
                       sa1_sf %>%
                         dplyr::select(sa1=SA1_MAIN11,
                                       geometry)) %>%
    dplyr::filter(!is.na(sa1))

   str_tdf <- st_join(str_tdf, 
                       beach_buffer %>%
                         dplyr::select(beach=id,
                                       geometry)) %>%
      mutate(beach = ifelse(is.na(beach), 0, beach))

    ltr_tdf <- st_join(ltr_tdf, 
                       beach_buffer %>%
                         dplyr::select(beach=id,
                                       geometry)) %>%
    mutate(beach = ifelse(is.na(beach), 0, beach))

```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  ## Add the submarket designations

   # Add individual classes
   str_tdf$geo_mrkt <- 'rural'
   str_tdf$geo_mrkt[str_tdf$sub_des == 'Middle'] <- 'suburban'
   str_tdf$geo_mrkt[str_tdf$sub_des == 'Inner'] <- 'city'
   str_tdf$geo_mrkt[str_tdf$suburb %in% core_suburbs] <- 'city-core'
   str_tdf$geo_mrkt[str_tdf$beach == 1] <- 'beach'
#   
#   # Order the factors properly
    str_tdf$geo_mrkt <- factor(str_tdf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban',
                                        'rural', 'beach'))

       # Add individual classes
   ltr_tdf$geo_mrkt <- 'rural'
   ltr_tdf$geo_mrkt[ltr_tdf$sub_des == 'Middle'] <- 'suburban'
   ltr_tdf$geo_mrkt[ltr_tdf$sub_des == 'Inner'] <- 'city'
   ltr_tdf$geo_mrkt[ltr_tdf$suburb %in% core_suburbs] <- 'city-core'
   ltr_tdf$geo_mrkt[ltr_tdf$beach == 1] <- 'beach'
#   
#   # Order the factors properly
   ltr_tdf$geo_mrkt <- factor(ltr_tdf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban',
                                        'rural', 'beach'))
 # Count Cleaning
   countCleaning('location')

The location of the short and long term rentals, colored by submarket, are shown below

#```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}
